[dcpo_gender_roles]: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles

### 2020-10-19 paper/dcpo_gender_roles.Rmd
adding lines

Gender egalitarianism does not have only one dimension but a multi-dimension.
Generating a measure of egalitarian gender roles without the classification may cause multidimensionality problem since people might have different opinions about gender roles by the dimensions.
For instance, some people have a more egalitarian veiw about the gender role in public sector rather than in private sector, while others do not.
To be specific, some might think that men and women should be treated and promoted equally at work, but that women should be in charge of housework.
Also, others may argue that both men and women can succeed as politicians, while saying that women are responsible for parenting.
If we disregard this kind of multi-dimensionality, we will not be able to measure gender egalitarianism properly in the various dimensions that people have.
The multi-dimensionality problem is relatively not salient if people in a society have an egalitarian view of all dimensions.
However, given that there are some variations of gender

After examining all questionnaires asking opinions about gender roles from series of cross-national surveys including World Value Survey (WVS) and surveys conducted in individual countries or regions such as Arab Barometer, Korean General Social Survey, etc.,

@@

egalitarian gender roles in the public sector which has been generally dominated by male, those in private sector where the role of female has been emphasized, the balance of female role in private and public sector, and male dominance over women.

>>>>

Gender egalitarianism does not have only one dimension but a multi-dimension.
Generating a measure of egalitarian gender roles without the classification may cause multidimensionality problem since people might have different opinions about gender roles by the dimensions.
For instance, some people have a more egalitarian veiw about the gender role in public sector rather than in private sector, while others do not.
To be specific, some might think that men and women should be treated and promoted equally at work, but that women should be in charge of housework.
Also, others may argue that both men and women can succeed as politicians, while saying that women are responsible for parenting.
The multi-dimensionality problem is relatively not salient if people in a society have an egalitarian view of all dimensions.
However, if we disregard this kind of multi-dimensionality given that there are some variations of gender egalitarain opinions by dimensions, we will not be able to measure gender egalitarianism properly in the various dimensions that people have.

After examining all questionnaires asking opinions about gender roles from series of cross-national surveys including World Value Survey (WVS) and surveys conducted in individual countries or regions such as Arab Barometer, Korean General Social Survey, etc., we classify them into four categories: 1) egalitarian gender roles in the public sector which has been generally dominated by male, 2) those in private sector where the role of female has been emphasized, 3) the balance of female role in private and public sector, and 4) male dominance over women.

@@
